### 2013-07-07 inst/doc/reml-blog-post.Rmd
documentation updated

## Why EML?

Archival, open data is great ... blah blah.  Good reuse is all about good Metadata blah blah...

@@

> Terence Parr once said "being an expert in XML is like being an expert in CSV".

@@

@@

### Current state of EML

* Generation of EML is limited.  e.g. to LTER centers with informatics support. 
* Applications of existing EML more limited still (?)

* Software to work with EML is limited to tools with low adoption rates across the community (e.g. Kepler).

 Researchers are isolated from the metadata encoding, instead providing plain-text descriptions in MS Word documents.  Allows for low barrier of entry but also makes a barrier to richer encoding.

### Promise of REML

### Authoring tools

### Parsing tools

### Publishing tools

>>>>

You know the spiel.  Archivally preserved open data is great [1]. For you [2], for your citations [3], for your grants, [4] and of course, for scientific progress more generally [5].

And you know that making data reusable is all really all about having good metadata [6-398].

@@

@@

You already use XML every day.  Microsoft office?  Those `.docx`, `xlsx`, etc., are just a bunch of XML files zipped together (just try `unzip file.docx`)  The tools are just good enough to hide the XML from you.  XML is so general that it's essentially meaningless to say a file is XML.  Could be anything. Terence Parr once said "being an expert in XML is like being an expert in CSV".

That's where schema come in.

@@

### 2013-07-07 inst/doc/reml.Rmd
documentation updated

@@

>>>>

Abstract

1. Recording good metadata is at the heart of effective data synthesis and reuse
2.

Vertically integrated repositories vs metadata driven repositories.

Data synthesis

## Why EML?

But specifying metadata is typically onerous, time-consuming and error prone.

Such definitions are also not machine readable.

Or at least, it doesn't have to be that way.  We just need better tools.

## Why REML?

@@

### Getting Started: A minimal example.

Imagine we are working with a `data.frame` in R analgous to Table 1.

<!--Writing a data.frame into EML -->

Writing this table into EML
